## Classification Trees

```{r}
options(tidyverse.quiet = TRUE)
library(titanic)
library(tidyverse)
library(tidymodels)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(rpart) #for classification trees
library(rpart.plot) #for plotting trees
library(RColorBrewer) #better visualization of classification trees
library(rattle) #better visualization of classification trees
```

Read in dataset   
```{r}
titanic = titanic::titanic_train
```

Structure and summary
```{r}
str(titanic)
summary(titanic)
```

Factor conversion and recoding (Always do this prior to splitting)  
```{r}
titanic = titanic %>% mutate(Survived = as_factor(Survived)) %>% 
  mutate(Survived = fct_recode(Survived, "No" = "0", "Yes" = "1" )) %>%
  mutate(Pclass = as_factor(Pclass)) %>% mutate(Sex = as_factor(Sex)) %>%
  mutate(Embarked = as_factor(Embarked)) %>% 
  mutate(Embarked = fct_recode(Embarked,"Unknown"="","Cherbourg"="C","Southampton"="S","Queenstown"="Q")) %>%
  select(Survived, Pclass, Sex, Age, SibSp, Parch, Fare, Embarked)

str(titanic)
```

```{r}
#select only variables relevant to our analysis
titanic = titanic %>% select(c("Survived","Pclass","Sex","Age","SibSp","Parch","Embarked"))

set.seed(1234)
imp_age = mice(titanic, m=5, method='pmm', printFlag=FALSE)
summary(imp_age)
```

Merge the imputed values into our titanic data frame. Imputation is part of the data cleaning process and should occur prior to splitting. 
```{r}
titanic_complete = complete(imp_age) 
summary(titanic_complete)
```

Splitting.  
```{r}
set.seed(123) 
titanic_split = initial_split(titanic_complete, prop = 0.7, strata = Survived) #70% in training
train = training(titanic_split) 
test = testing(titanic_split)
```

Now that we have the split data, let's build a classification tree. Here we use caret to manage the model building.  
```{r}
titanic_recipe = recipe(Survived ~ Age, train)

tree_model = decision_tree() %>% 
  set_engine("rpart", model = TRUE) %>% #don't forget the model = TRUE flag
  set_mode("classification")

titanic_wflow = 
  workflow() %>% 
  add_model(tree_model) %>% 
  add_recipe(titanic_recipe)

titanic_fit = fit(titanic_wflow, train)
```

Let's take a look at our tree (a few ways)  
```{r}
#look at the tree's fit
titanic_fit %>%
  pull_workflow_fit() %>%
  pluck("fit")  
```
```{r}
#extract the tree's fit from the fit object
tree = titanic_fit %>% 
  pull_workflow_fit() %>% 
  pluck("fit")

#plot the tree
rpart.plot(tree)
```
```{r}
#alternative
fancyRpartPlot(tree) 
```
Look at the "rpart" complexity parameter "cp".    
```{r}
titanic_fit$fit$fit$fit$cptable
```





