## Another Random Forest

```{r, include = FALSE}
library(tidyverse)
library(tidymodels)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(ranger) #for random forests
library(randomForest) #also for random forests
library(caret)
library(skimr)
library(GGally)
library(gridExtra)
library(vip) #variable importance
```

Load data from the CSData.csv file.  
```{r}
churn = read_csv("churn-1.csv")
```

Structure and summary
```{R}
str(churn)
summary(churn)
```
Delete customer ID column  
```{r}
churn = churn %>% select(-customerID)
```

Convert all character variables to factors  
```{r}
churn = churn %>% mutate_if(is.character,as_factor)
```

```{r}
str(churn)
```
```{r}
churn = churn %>% mutate(SeniorCitizen = as_factor(SeniorCitizen)) %>%
  mutate(SeniorCitizen = fct_recode(SeniorCitizen, "No" = "0", "Yes" = "1"))
str(churn)
```
Check for missing data 
```{r}
skim(churn)
```
Only missingness is in TotalCharges. Very small percentage. Row-wise deletion should be fine.  
```{r}
churn = churn %>% drop_na()
```

Now we'll split the data.  
```{r}
set.seed(123) 
churn_split = initial_split(churn, prop = 0.7, strata = Churn) #70% in training
train = training(churn_split)
test = testing(churn_split)
```

Visualization  
```{r}
p1 = ggplot(train, aes(x = gender, fill = Churn)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = SeniorCitizen, fill = Churn)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = Partner, fill = Churn)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = Dependents, fill = Churn)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```
```{r}
p1 = ggplot(train, aes(x = PhoneService, fill = Churn)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = MultipleLines, fill = Churn)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = InternetService, fill = Churn)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = OnlineSecurity, fill = Churn)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
p1 = ggplot(train, aes(x = OnlineBackup, fill = Churn)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = DeviceProtection, fill = Churn)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = TechSupport, fill = Churn)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = StreamingTV, fill = Churn)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
p1 = ggplot(train, aes(x = StreamingMovies, fill = Churn)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = Contract, fill = Churn)) + geom_bar(position = "fill")
p3 = ggplot(train, aes(x = PaperlessBilling, fill = Churn)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = PaymentMethod, fill = Churn)) + geom_bar(position = "fill")
grid.arrange(p1,p2,p3,p4)
```

```{r}
p1 = ggplot(train, aes(x = Churn, y = tenure)) + geom_boxplot()
p2 = ggplot(train, aes(x = Churn, y = MonthlyCharges)) + geom_boxplot()
p3 = ggplot(train, aes(x = Churn, y = TotalCharges)) + geom_boxplot()
grid.arrange(p1,p2,p3, ncol = 2)
```
Random forest  
```{r}
churn_recipe = recipe(Churn ~., train) %>%
  step_dummy(all_nominal(), -all_outcomes())

rf_model = rand_forest() %>% 
  set_engine("ranger", importance = "permutation") %>% #added importance metric
  set_mode("classification")

churn_wflow = 
  workflow() %>% 
  add_model(rf_model) %>% 
  add_recipe(churn_recipe)

set.seed(123)
churn_fit = fit(churn_wflow, train)
```

Predictions  
```{r}
trainpredrf = predict(churn_fit, train)
head(trainpredrf)
```

Confusion matrix
```{r}
confusionMatrix(trainpredrf$.pred_class, train$Churn, 
                positive = "Yes")
```

Predictions on test
```{r}
testpredrf = predict(churn_fit, test)
head(testpredrf)
confusionMatrix(testpredrf$.pred_class, test$Churn, 
                positive = "Yes")
```

Save the model to a file to load later (if needed)  
```{r}
saveRDS(churn_fit, "churn_fit.rds")
```

Load the model  
```{r}
churn_fit = readRDS("churn_fit.rds")
```

Check out variable importance
```{r}
churn_fit %>% pull_workflow_fit() %>% vip(geom = "point")
```







