## Classification Tree (Another example)

Libraries  
```{r}
library(tidyverse)
library(tidymodels)
library(rpart) #for classification trees
library(rpart.plot) #plotting trees
library(RColorBrewer) #better visualization of classification trees
library(rattle) #better visualization of classification trees
library(caret) #for easy confusion matrix creation 
```

Load data from the CSData.csv file.  
```{r}
credit = read_csv("CSData (1).csv")
```

Structure and summary
```{r}
str(credit)
summary(credit)
```

Factor conversion. Convert the response variable SeriousDlqin2yrs.
```{r}
credit = credit %>% mutate(SeriousDlqin2yrs = as_factor(SeriousDlqin2yrs)) %>% 
  mutate(SeriousDlqin2yrs = fct_recode(SeriousDlqin2yrs, "No" = "0", "Yes" = "1" )) 

str(credit)
```

Data cleaning (same as done in earlier lectures).  
```{r}
credit = credit %>% filter(RevolvingUtilizationOfUnsecuredLines < 2)
credit = credit %>% filter(DebtRatio < 5)
credit = credit %>% filter(MonthlyIncome < 20000) %>% drop_na()
credit = credit %>% filter(NumberOfOpenCreditLinesAndLoans < 40)
credit = credit %>% filter(NumberOfTimes90DaysLate < 10)
credit = credit %>% filter(NumberRealEstateLoansOrLines < 10)
credit = credit %>% filter(NumberOfDependents < 10)
```

Now we'll split the data.  
```{r}
set.seed(123) 
credit_split = initial_split(credit, prop = 0.7, strata = SeriousDlqin2yrs) #70% in training
train = training(credit_split)
test = testing(credit_split)
```

Let's build a classification tree.  
```{r}
credit_recipe = recipe(SeriousDlqin2yrs  ~., train)

tree_model = decision_tree() %>% 
  set_engine("rpart", model = TRUE) %>% #don't forget the model = TRUE flag
  set_mode("classification")

credit_wflow = 
  workflow() %>% 
  add_model(tree_model) %>% 
  add_recipe(credit_recipe)

credit_fit = fit(credit_wflow, train)
```

```{r}
#extract the tree's fit from the fit object
tree = credit_fit %>% 
  pull_workflow_fit() %>% 
  pluck("fit")

#plot the tree
fancyRpartPlot(tree)
```

Look at the "rpart" complexity parameter "cp".    
```{r}
credit_fit$fit$fit$fit$cptable
```
Look at performance of this simple tree.

Predictions on training set  
```{r}
treepred = predict(credit_fit, train, type = "class")
head(treepred)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred$.pred_class,train$SeriousDlqin2yrs,positive="Yes") #predictions first then actual
```

Predictions on testing set  
```{r}
treepred_test = predict(credit_fit, test, type = "class")
head(treepred_test)
```

Caret confusion matrix and accuracy, etc. calcs  
```{r}
confusionMatrix(treepred_test$.pred_class,test$SeriousDlqin2yrs,positive="Yes") #predictions first then actual
```




