## Regression with Categorical Variables

Libraries  
```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
```

Read in the data
```{r}
college = read_csv("College.csv")
glimpse(college)
```

We'll leave school as is (we do not actually use it in our modeling). We do use "Type" which is currently a character type variable. Let's use mutate to convert to a factor.  
```{r}
college = college %>% mutate(Type = as_factor(Type))
str(college)
```

Visualize relationships and look at correlation (note: correlation is not calculated for non-quantitative variables like "School" and "Type"). The variable we will ultimately try predict is "GradPercent".   
```{r}
ggpairs(college, columns = c(2:7)) #exclude the 1st column which contains "School"
```

Closer look at "Type" and "GradPercent".  
```{r}
ggplot(college, aes(x=Type,y=GradPercent)) + geom_boxplot() + theme_bw()
ggplot(college, aes(x=Type,y=GradPercent)) + geom_boxplot() + 
  geom_jitter() + theme_bw()
```

Model - Type predicts GradPercent  
```{r}
grad_recipe = recipe(GradPercent ~ Type, college) %>%
  step_dummy(Type)

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(grad_recipe)

lm_fit = fit(lm_wflow, college)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
84.120 - 1.787*Type_University

Prediction by Type  
```{r}
predict(lm_fit, new_data = data.frame(Type = c("Lib Arts","University")))
```

An example with multiple levels in a categorical variable.  
```{r}
flower = iris #built-in dataset
str(flower)
```

Visualize/correlate  
```{r}
ggpairs(flower)
```

Model  (Species to predict Sepal.Length)
```{r}
iris_recipe = recipe(Sepal.Length ~ Species, flower) %>%
  step_dummy(Species)

lm_model2 = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow2 = 
  workflow() %>% 
  add_model(lm_model2) %>% 
  add_recipe(iris_recipe)

lm_fit2 = fit(lm_wflow2, flower)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```
5.0060 + (0.93)(Versicolor) + (1.582)(Virginica)

Predictions:   
```{r}
predict(lm_fit2, new_data = data.frame(Species = c("setosa","versicolor","virginica")))
```
Traditional linear regression diagnostics are less meaningful for categorical variables.  


