## Interaction Effects in Regression

Interactions --> The effect of one variable is dependent on the value of another.

Libraries
```{r}
library(tidyverse) #tidyverse set of packages and functions
library(tidymodels)
library(glmnet) #for Lasso, ridge, and elastic net models 
library(GGally) #create ggcorr and ggpairs plots
library(ggcorrplot) #create an alternative to ggcorr plots
library(MASS) #access to forward and backward selection algorithms
library(leaps) #best subset selection
library(lmtest) #for the dw test
library(splines) #for nonlinear fitting
```

Read in data and examine structure
```{r}
birth = read_csv("birth_smoker-1.csv")
summary(birth)
str(birth)
```
```{r}
birth = birth %>% mutate(smoker = as_factor(smoker))
```


Plots  
```{r}
ggplot(birth,aes(x=gestation,y=weight)) + geom_point() + theme_bw()
```
Clearly, gestation length affects weight. Longer gestation --> higher weight. How about smoking?  
```{r}
ggplot(birth,aes(x=smoker,y=weight)) + geom_boxplot() + theme_bw()
```
Clearly, smoking leads to lower birth weights.  

Let's look at one more plot to see how all of these variables interact.  
```{r}
ggplot(birth,aes(x = gestation,y = weight, color = smoker)) + 
  geom_point() + geom_smooth(method='lm', se = FALSE)+ theme_bw()
```

We have a couple of ways that we can approach this. Let's look at a model with "gestation" and "smoker" to predict "weight".  

```{r}
birth_recipe = recipe(weight ~ gestation + smoker, birth) %>%
  step_dummy(all_nominal())

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(birth_recipe)

lm_fit = fit(lm_wflow, birth)
```

```{r}
summary(lm_fit$fit$fit$fit)
```
Both gestation and smoker are significant. Being a smoker has a negative impact on weight.  

From our plot above it looks like there might be a slight difference in the slopes of the regression lines by group. Let's add an interaction effect to the model and see what we get. 
```{r}
birth_recipe = recipe(weight ~ gestation + smoker, birth) %>%
  step_dummy(all_nominal()) %>%
  step_interact(~gestation:starts_with("smoker_"))

lm_model = #give the model type a name 
  linear_reg() %>% #specify that we are doing linear regression
  set_engine("lm") #specify the specify type of linear tool we want to use 

lm_wflow = 
  workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(birth_recipe)

lm_fit2 = fit(lm_wflow, birth)
```

```{r}
summary(lm_fit2$fit$fit$fit)
```
No apparent interaction (i.e., the slope of the regression lines by smoker group are not significantly different).  

